quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Started adding the data set table

Add a table of data sets that quollr have

>>>>

The `quollr` package comes with several data sets that load with the package. These are described in Table `r knitr::asis_output(ifelse(knitr::is_html_output(), '\\@ref(tab:datasets-tb-html)', '\\@ref(tab:datasets-tb-pdf)'))`.

```{r}
datasets_tb <- tibble(dt = c("scurve",
                             "scurve_umap",
                             "scurve_umap_predict",
                             "scurve_umap2",
                             "scurve_umap3",
                             "scurve_umap4",
                             "scurve_umap5",
                             "scurve_umap6",
                             "scurve_model_obj",
                             "scurve_umap_mse",
                             "scurve_umap_mse2",
                             "scurve_umap_mse3",
                             "scurve_umap_mse4",
                             "scurve_umap_mse5",
                             "scurve_umap_mse6"), 
                      text = c("scurve",
                             "scurve_umap",
                             "scurve_umap_predict",
                             "scurve_umap2",
                             "scurve_umap3",
                             "scurve_umap4",
                             "scurve_umap5",
                             "scurve_umap6",
                             "scurve_model_obj",
                             "scurve_umap_mse",
                             "scurve_umap_mse2",
                             "scurve_umap_mse3",
                             "scurve_umap_mse4",
                             "scurve_umap_mse5",
                             "scurve_umap_mse6"))
```

```{r datasets-tb-html, eval=knitr::is_html_output()}
datasets_tb |> 
  kable(caption = "cardinalR data sets", col.names = c("data", "explanation")) 
```

```{r datasets-tb-pdf, eval=knitr::is_latex_output()}
datasets_tb |> 
  kable(caption = "cquollr data sets", format="latex", col.names = c("data", "explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

### 2025-05-12 paper-quollr.tex
Started adding the data set table

Add a table of data sets that quollr have

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-18-1}

@@

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-27-1}

>>>>

The \texttt{quollr} package comes with several data sets that load with the package. These are described in Table \ref{tab:datasets-tb-pdf}.

\begin{table}

\caption{\label{tab:datasets-tb-pdf}cquollr data sets}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
data & explanation\\
\midrule
scurve & scurve\\
scurve\_umap & scurve\_umap\\
scurve\_umap\_predict & scurve\_umap\_predict\\
scurve\_umap2 & scurve\_umap2\\
scurve\_umap3 & scurve\_umap3\\
\addlinespace
scurve\_umap4 & scurve\_umap4\\
scurve\_umap5 & scurve\_umap5\\
scurve\_umap6 & scurve\_umap6\\
scurve\_model\_obj & scurve\_model\_obj\\
scurve\_umap\_mse & scurve\_umap\_mse\\
\addlinespace
scurve\_umap\_mse2 & scurve\_umap\_mse2\\
scurve\_umap\_mse3 & scurve\_umap\_mse3\\
scurve\_umap\_mse4 & scurve\_umap\_mse4\\
scurve\_umap\_mse5 & scurve\_umap\_mse5\\
scurve\_umap\_mse6 & scurve\_umap\_mse6\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-20-1}

@@

\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-28-1}
